|

### 2021-12-17 05-Chp-CPRD-Analysis.Rmd
Sort todos

<!----------------------------------------------------------------------------->
<!-- TODO Check table caption -->

@@

<!-- TODO Check this table title -->

(ref:statinTypeTable-caption) __Summary of statin properties__ Number of patients prescribed lipophilicity vs hydrophilicity statins, by grouped year of prescription.

>>>>

<!----------------------------------------------------------------------------->

@@

(ref:statinTypeTable-caption) __Summary of statin properties__ - Number of patients prescribed lipophilicity vs hydrophilicity statins, by grouped year of prescription.

### 2021-12-17 06-Chp-IPD-Analysis.Rmd
Sort todos

<!-- TODO Should start with inclusion criteria -->

@@

<!-- TODO Ensure that the results are actually on the mmol/L scale -->

@@

Nine cohorts (8 DPUK only, 1 Systematic review + DPUK) responded positively to requests for data access. However, on inspection of data provided, six of these cohorts were excluded and the reason for exclusion in each case is shown in Table \@ref(tab:dataExcluded-table). In summary, two cohorts contained were memory-complaint cohorts, containing participants unlikely to be free of dementia at baseline (BRACE, MEMENTO). Two cohorts, despite being designed as multi-wave studies, only shared data related to a single wave and so represented cross-sectional data (Generation Scotland, NICOLA). Finally TRACK HD is a genetic cohort where cohort owners advised me that dementia will inevitably develop in mid-life driven by the Huntington's (HTT gene) mutation and that this effect would likely far outweigh the effect of lipids. Finally, the ELSA study was excluded based on the dichotomous definition of the exposure variable. <!-- TODO CITATION NEEDED for each study here! -->

@@

<!-- TODO Be clear on the different types of databases, e.g., those where users are followed up regularly vs. those where participants are captured via EHR-->

<!-- TODO Need to talk about how dementia was assessed in each! -->

<!-- TODO Link to appendix about data sources not approached -->

@@

<!-- TODO Now that using a fixed effect model, evidence of TG/ACD association -->

@@

<!-- TODO May need to talk about other confounders here -->

@@

<!-- TODO Talk about the fact that I used multiple imputation and they did not. Evidenced by wider confidence intervals, indicating a smaller sample size, likely the result of a complete case -->

@@

<!-- REVIEW Or a requirement of peer review and publication be that the data be recorded centrally and made available through a coordinated application process) -->

>>>>

@@

@@

Nine cohorts (8 DPUK only, 1 Systematic review + DPUK) responded positively to requests for data access. However, on inspection of data provided, six of these cohorts were excluded and the reason for exclusion in each case is shown in Table \@ref(tab:dataExcluded-table). In summary, two cohorts contained were memory-complaint cohorts, containing participants unlikely to be free of dementia at baseline (BRACE, MEMENTO). Two cohorts, despite being designed as multi-wave studies, only shared data related to a single wave and so represented cross-sectional data (Generation Scotland, NICOLA). Finally TRACK HD is a genetic cohort where cohort owners advised me that dementia will inevitably develop in mid-life driven by the Huntington's (HTT gene) mutation and that this effect would likely far outweigh the effect of lipids. Finally, the ELSA study was excluded based on the dichotomous definition of the exposure variable.

@@

@@

@@

@@

@@

### 2021-12-17 07-Chp-Triangulation.Rmd
Sort todos

<!-- TODO Add this to the Chapter summary in the introduction -->

<!-- ### Triangulation  -->

<!-- TODO Have a look at this - potentially move to triangulation chapter -->

<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->

<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework. Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the. For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated. [@guyatt2011] -->

@@

The triangulation exercises presented in this chapter draw on the research produced in each of the preceding chapters. More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading). This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-analysis-heading)) and the association of lipids with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).

@@

<!-- TODO Update this paragraph to reflect extra 2 MR studies -->

From the data sources identified in Section \@ref(tri-data-sources), I identified 18 results relevant to my first causal question of interest. Most (N =17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate via the CPRD analysis.  The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.

<!-- TODO Double check this reference list is correct! -->

>>>>

<!-- IDEA Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework. Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the. For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated. [@guyatt2011] -->

@@

The triangulation exercises presented in this chapter draw on the research produced in each of the preceding chapters. More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading). This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-analysis-heading)) and the association of lipids (namely, total cholesterol (TC), high-density lipoprotein cholesterol (HDL), low-density lipoprotein cholesterol (LDL) and triglycerides (TG)) with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).

@@

From the data sources identified in Section \@ref(tri-data-sources), I identified 21 results relevant to my first causal question of interest. Most (N = 20) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate via the CPRD analysis.  The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
